%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Souvik De} \\ \vspace{1pt}
    \href{mailto:souvikde.ns@gmail.com}{\underline{souvikde.ns@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/souvik-de-a2b941169/}{\underline{linkedin.com/in/Souvikns}} $|$
    \href{https://github.com/Souvikns}{\underline{github.com/Souvikns}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {AsyncAPI}{Remote}
      {Maintainer of CLI repo}{June 2021 -- Ongoing}
      \resumeItemListStart
         \resumeItem{Using Typescript, React and InkJs to build a CLI tool that will support all other CLI's provided by AsyncAPI. }
         \resumeItem{Working with the core team to improve and maintain the CLI.}
         \resumeItem{Offered a paid internship for two months where I worked on building Spec file loader for the CLI.}
     \resumeItemListEnd
     
     \resumeSubheading
     {UpTone}{Remote}
      {Worked as a backend developer}{August 2021 -- Ongoing}
      \resumeItemListStart
         \resumeItem{Building a express API for the Uptone client(which is a mobile app). }
         \resumeItem{This is a unpaid work where I work for 7 to 8 hours a week.}
         \resumeItem{Mostly write code and review work of other team members.}
     \resumeItemListEnd

    
  \resumeSubHeadingListEnd
  


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/asyncapi/cli} {AsyncAPI CLI: CLI to work with your AsyncAPI file}}{[ ReactJS, InkJS, Node, TypeScript]}}{June 2021}
          \resumeItemListStart
            \resumeItem{ Working as a Maintainer for the project, contributing to code and managing overall development.}
            \resumeItem{ Implemented config context for the CLI to seamlessly load specfile and increase UX. }
            \resumeItem{ Brainstormed and successfully, managing and developing the product.}
            \resumeItem{ Working closely with the core AsyncAPI team. }
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
     \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/Souvikns/ink-router-cli}{Ink Router CLI : A react-router style CLI parser for InkJS}} {[React, Data Structures, InkJS]}}{March 2020}
          \resumeItemListStart
            \resumeItem{Took inspiration from core \href{https://github.com/remix-run/react-router}{\underline{react-router}} to create a declarative routing for InkJS. }
            \resumeItem{Learned core react types to build the declarative routing. }
          \resumeItemListEnd
    \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/Souvikns/notion-board}{\textbf{Notion Board}}}{ [NodeJS, TypeScript, GitHub Action, Notion API]}}{April 2021}
          \resumeItemListStart
            \resumeItem{A GitHub action to sync GitHub issues with Notion database. }
            \resumeItem{Build when Notion API was released. }
            \resumeItem{Created as a fun project to learn GitHub actions.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, HTML/CSS} \\
     \textbf{Frameworks}{: Express, React, Node.js, Airtable API, Material-UI, Electron, NextJs, Firebase  } \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, AsyncAPI, OpenAPI, Postman} \\
     \textbf{Libraries}{: React-Router, MongooseJS, Newman }
    }}
 \end{itemize}


%-------------------------------------------
\section{Awards and Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small\item{\resumeItemListStart
           \resumeItem{\textbf{\href{https://drive.google.com/file/d/1NjTX2drZ3M4xpm8oKZ7bV4YLU-jEU3fY/view?usp=sharing}{Machine Learning Competition}}: Qalified a zonal round competition on Machine Learning and AI conducted by Diginique TechLabs in association with Cognizance IIT Roorkee. }
      \resumeItemListEnd
    }
 \end{itemize}
 
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small\item{\resumeItemListStart
           \resumeItem{\textbf{\href{https://badgr.com/public/assertions/nfX4O89DRPevyH1r0tMyBQ?identity__email=souvikde.ns@gmail.com}{Postman Student Expert}}: Postman Student Experts are proficient in the essential skills involved in building and testing API requests in Postman. }
      \resumeItemListEnd
    }
 \end{itemize}
 
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Chandigarh University}{Mohali, Punjab}
      {Junior,B.E in Computer Science and Engineering}{August 2018 -- Expected July. 2022}
  \resumeSubHeadingListEnd




\end{document}
